### 2013-03-15 doc/final_report/testing.tex
Added some blurb about unit testing to final report

>>>>

In cases where Partridge calls remote services, reuses code that has already
been tested, or calls code that runs heavy computation, it can be inconvenient
or unhelpful to run unit tests that trigger these behaviours. To save time,
\emph{Mock}\cite{mock2013} was used for verifying these behaviours were being
called correctly instead.  \emph{Mock} allows the arbitrary replacement of Python
routines and objects with `mock' objects that mimic the behaviour of the
original routine and store information on how they were called or used. This
meant that calls to long-running routines and functions that already have tests
can be validated and a fake return value sent back to the caller, without
having to actually execute the code. This technique was used heavily in the
paper processor which calls SAPIENTA and PDFX and also wraps several data
classes which have their own unit tests.
